\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-06 cfhtlens.tex
Fig 2 caption and description changed

\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the mass aperture statistic, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs statistics \citep{schneider/etal:2010}.  Figure~\ref{fig:filters} shows the integrands of these statistics (i.e. the weights placed on each $\ell$ scale),  for two cases, normalised to their maximum value.  The right panel shows the integrand\footnote{Note that the lower left panel of Fig. 1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum
angular separation of $100'$. However, in \citet{kilbinger/etal:2013}, the data used in \citet{kitching/etal:2016}, 
the maximum $\theta$ is $350'$.} of $\xi_+$ for $\theta=100'$ and $\theta=350'$. The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.  Finally, the left panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.

@@

\begin{figure}[htb]
\begin{center}
\begin{tabular}{ccc}
\includegraphics[width=0.31\textwidth]{figures/IntegKsip.pdf} &
\includegraphics[width=0.31\textwidth]{figures/IntegCOSEBIs.pdf} &
\includegraphics[width=0.31\textwidth]{figures/IntegMap.pdf}
\end{tabular}
\caption{ \label{fig:filters}. Integrand of $\xi_+$, $E_1$ (E-COSEBIs) and $M^2_{\rm ap}$, respectively.
Two cases are shown for each statistic as listed in each caption.
For the aperture mass statistic $\theta_{\rm max}=2\theta$ is shown. 
Note that higher order COSEBIs modes generally probe larger $\ell$-modes, hence here we only show the lowest mode $E_1$. All values are normalized with respect to their maximum value. 
}
\end{center}
\end{figure}

>>>>

\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the aperture-mass dispersion, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs \citep{schneider/etal:2010}.  Figure~\ref{fig:filters} shows the integrands of these statistics 
% (i.e. the weights placed on each $\ell$ scale),  
for two cases, normalised to their maximum value.  The integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)=J_0(\ell)$ for $\xi_+$, $F(\ell)= U^2_\theta(\ell)$ for  $M_ {\rm ap}^2$ \citep[see][]{schneider/etal:1998} and $F(\ell)=W_n(\ell)$ for COSEBIs \citep[see][]{schneider/etal:2010}. For $\xi_\pm$, $P(\ell)$ is equal to the sum of the E and B-mode convergence power spectra. This is one of the main motivators for the development of aperture-mass dispersion. However, $M_ {\rm ap}^2$ statistics is a lossy conversion and is biased by small angular separations,
where blending of galaxies makes shear measurement challenging/impossible \citep{Kilbinger/etal:2006}. As a result, COSEBIs was developed which tackles both shortcomings of $M_ {\rm ap}^2$ statistics.
The right panel shows the integrand\footnote{Note that the lower left panel of Fig. 1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum angular separation of $100'$. However, in \citet{kilbinger/etal:2013}, the data used in \citet{kitching/etal:2016}, $\theta$ is between $0.8'$ and $350'$.} of $\xi_+$ for $\theta=100'$ and $\theta=350'$. The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.  Finally, the left panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.

@@

\begin{figure}[htb]
\begin{center}
\begin{tabular}{ccc}
\includegraphics[width=0.31\textwidth]{figures/IntegKsip.pdf} &
\includegraphics[width=0.31\textwidth]{figures/IntegCOSEBIs.pdf} &
\includegraphics[width=0.31\textwidth]{figures/IntegMap.pdf}
\end{tabular}
\caption{ \label{fig:filters}. Integrand of $\xi_+$, $E_1$ (E-COSEBIs) and $M^2_{\rm ap}$, respectively.
All integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)$ is the corresponding weight-function
for each statistic and $P(\ell)$ is the E-mode convergence power spectrum, with the exception of $\xi_+$, for which
$P(\ell)$ is equal to the sum of E and B-mode power spectra. 
Two cases are shown for each statistic as listed in each caption.
For the aperture mass statistic $\theta_{\rm max}=2\theta$ is shown. 
Note that higher order COSEBIs modes generally probe larger $\ell$-modes, 
hence here we only show the lowest mode $E_1$. All values are normalized with respect to their maximum value. 
}
\end{center}
\end{figure}
